Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-15 grove-paper.tex
Updates from Overleaf

@@

Of course, if the user wants a genuine copy
and not just a move, that can easily be achieved
(TODO: figure for this?)

@@

Restore isn't a copy, it is a move

@@

For example, consider the graphs in Figure~\ref{fig:Editing Different Parts of the Code}.
The

A + B make edits and transmit to C, C is able to resolve without any assistance, 
order that the edits are received doesn't matter you get the same program state
at the end

commutativity

\begin{figure}
\centering
TODO: commutativity diagram of screenshots with two cursors
\caption{TODO:Caption}
\label{fig:Screenshot0}
\end{figure}

>>>>

Note that we do not explicitly delete or add vertexes.
Our only actions are deleting or adding \textit{edges}.
Vertexes are implicitly created whenever an edge
is created that points to it.
Deleting vertexes is not necessary, as we can simply
remove the edge pointing to it.

@@

Of course, if the user wants a genuine copy
and not just a move, that can be achieved
by creating new vertexes with fresh identifiers.
(TODO: figure for this?)

@@

@@

For example, suppose there are users, A and B,
that are synchronized with each other and
have the code \texttt{3 + 4}.
That is to say, they both have
the top graphs in Figure~\ref{fig:Editing Different Parts of the Code}.

Next, suppose user A changes the \texttt{3} to a \texttt{13},
and user B changes the \texttt{4} to a \texttt{14}.
Before transmitting their edits to each other,
user A thus has left graph and user B has the right graph.
For user A, this involves deleting edge~7 and creating edge~14.
For user B, this involves deleting edge~10 and creating edge~18.

To merge these two graphs each user simply replays the edge deletions and additions
that the other user performed.

Both user then have the bottom graph and are again synchronized with each other.

Note that aside from transmitting the edge deletions and additions,
no coordination between A and B is needed to coordinate the merge.
For example, suppose that A and B did not transmit their edits to each other
but to a third user, C, that has the original graph at the top of Figure~\ref{fig:Editing Different Parts of the Code}.
User C can replay the edits from A and B in any order and will always get
the graph at the bottom of Figure~\ref{fig:Editing Different Parts of the Code}.

Stated more formally, our edit model obeys commutativity
as shown in Figure~\ref{fig:Commutativity}.
For any two sequences of edits $\vec{\alpha}$ and $\vec{\alpha}^\prime$,
applying them in either order produces the same results.

\begin{figure}
\centering
TODO: commutativity diagram of screenshots with two cursors
\caption{TODO:Commutativity}
\label{fig:Commutativity}
\end{figure}
